Synthesizing Symmetric Lenses

### 2018-07-05 papers/SymmetricLenses/main.tex
Found error in Theorem 3 but still stuck

Observe that 
$$
V_{ \MergeROf{\Lens_1}{\Lens_2}}(s) = \{t \in \mathcal{L}(T) \; | \;  \MergeROf{\Lens_1}{\Lens_2}.\ell.\PutROf{s}{t} = t\}
$$
If $s \in \mathcal{L}(S_1)$, then
$$
V_{ \MergeROf{\Lens_1}{\Lens_2}}(s) = \{t \in \mathcal{L}(T) \; | \;  \ell_1.\PutROf{s}{t} = t\} = V_{\ell_1}(s)
$$
while if $s \in \mathcal{L}(S_2)$, then
$$
V_{ \MergeROf{\Lens_1}{\Lens_2}}(s) = \{t \in \mathcal{L}(T) \; | \;  \ell_2.\PutROf{s}{t} = t\} = V_{\ell_2}(s)
$$
Consequently,
\begin{align*}
&\sum_{s \in \mathcal{L}(S_1 \; |_p \; S_2)}P_{S_1 \; |_p \; S_2}(s) H(V_{\MergeROf{\Lens_1}{\Lens_2}}(s))\\
&= p * \sum_{s \in \mathcal{L}(S_1)}P_{S_1}(s) H(V_{\ell_1}(s)) + (1-p) * \sum_{s \in \mathcal{L}(S_2)}P_{S_2}(s) H(V_{\ell_2}(s))\\
&= p * (\mathbb{H}^{\rightarrow}(S_1 \; | \; \ell_1,T_1) ) + (1-p) * (\mathbb{H}^{\rightarrow}(S_2 \; | \; \ell_2,T_2) )
\end{align*}
\item
($S = \MergeLOf{\Lens_1}{\Lens_2}$)

Observe that 
\begin{align*}
V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s) &= \{t \in \mathcal{L}(T_1 \; |_q \; T_2) \; | \;  \MergeLOf{\Lens_1}{\Lens_2}.\PutROf{s}{t} = t\}\\
&= \{t \in \mathcal{L}(T_1 \; |_q \; T_2) \; | \;  \ell_1.\PutROf{s}{t} = t \text{ or } \ell_2.\PutROf{s}{t} = t\}\\
&= V_{\ell_1}(s) \cup V_{\ell_2}(s)
\end{align*}
First we consider $H(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))$:
\begin{align*}
H(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)) &= \sum_{t \in V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}P_{V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}(t) \log_2 P_{V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}(t)\\
&= \sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}\frac{q * P_{T_1}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))} \log_2 \frac{q * P_{T_1}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))} \\
&+ \sum_{t \in \mathcal{L}(T_2) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}\frac{(1-q) * P_{T_2}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))} \log_2 \frac{(1-q) * P_{T_2}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}
\end{align*}
We focus on the term 
$$\sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}\frac{q * P_{T_1}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))} \log_2 \frac{q * P_{T_1}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}$$
Observe that
\begin{align*}
&\sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}\frac{q * P_{T_1}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))} \log_2 \frac{q * P_{T_1}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\\
&= \frac{q}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}P_{T_1}(t) \log_2 q * P_{T_1}(t)\\
&- \frac{q * \log_2 P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}P_{T_1}(t)
\end{align*}
Again we focus on the term
$$\sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}P_{T_1}(t) \log_2 q * P_{T_1}(t)$$
Observe that
\begin{align*}
\sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}P_{T_1}(t) \log_2 q * P_{T_1}(t) &= \log_2 q * P_{T_1}(V_{\ell_1}(s)) + H(V_{\ell_1}(s))
\end{align*}
Hence
\begin{align*}
&\sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}\frac{q * P_{T_1}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))} \log_2 \frac{q * P_{T_1}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))} \\
&= \frac{q}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}P_{T_1}(t) \log_2 q * P_{T_1}(t)\\
&- \frac{q * \log_2 P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}P_{T_1}(t)\\
&= \frac{q \left[P_{T_1}(V_{\ell_1}(s)) \left[\log_2 \frac{q}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))} \right] + H(V_{\ell_1}(s))\right]}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}
\end{align*}
Similarly,
\begin{align*}
&\sum_{t \in \mathcal{L}(T_2) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}\frac{(1-q) * P_{T_2}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))} \log_2 \frac{(1-q) * P_{T_2}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\\
&= \frac{(1-q)\left[P_{T_2}(V_{\ell_2}(s)) \left[\log_2 \frac{(1-q)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\right] + H(V_{\ell_2}(s))\right]}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}
\end{align*}
\end{enumerate}

>>>>

Observe that 
$$
V_{ \MergeROf{\Lens_1}{\Lens_2}}(s) = \{t \in \mathcal{L}(T) \; | \;  \MergeROf{\Lens_1}{\Lens_2}.\PutROf{s}{t} = t\}
$$
If $s \in \mathcal{L}(S_1)$, then
$$
V_{ \MergeROf{\Lens_1}{\Lens_2}}(s) = \{t \in \mathcal{L}(T) \; | \;  \ell_1.\PutROf{s}{t} = t\} = V_{\ell_1}(s)
$$
while if $s \in \mathcal{L}(S_2)$, then
$$
V_{ \MergeROf{\Lens_1}{\Lens_2}}(s) = \{t \in \mathcal{L}(T) \; | \;  \ell_2.\PutROf{s}{t} = t\} = V_{\ell_2}(s)
$$
Consequently,
\begin{align*}
&\sum_{s \in \mathcal{L}(S_1 \; |_p \; S_2)}P_{S_1 \; |_p \; S_2}(s) H(V_{\MergeROf{\Lens_1}{\Lens_2}}(s))\\
&= p * \sum_{s \in \mathcal{L}(S_1)}P_{S_1}(s) H(V_{\ell_1}(s)) + (1-p) * \sum_{s \in \mathcal{L}(S_2)}P_{S_2}(s) H(V_{\ell_2}(s))\\
&= p * (\mathbb{H}^{\rightarrow}(S_1 \; | \; \ell_1,T_1) ) + (1-p) * (\mathbb{H}^{\rightarrow}(S_2 \; | \; \ell_2,T_2) )
\end{align*}
\item
($S = \MergeLOf{\Lens_1}{\Lens_2}$)

Observe that 
\begin{align*}
V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s) &= \{t \in \mathcal{L}(T_1 \; |_q \; T_2) \; | \;  \MergeLOf{\Lens_1}{\Lens_2}.\PutROf{s}{t} = t\}\\
&= \{t \in \mathcal{L}(T_1 \; |_q \; T_2) \; | \;  \ell_1.\PutROf{s}{t} = t \text{ or } \ell_2.\PutROf{s}{t} = t\}\\
&= V_{\ell_1}(s) \cup V_{\ell_2}(s)
\end{align*}
First we consider $H(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))$:
\begin{align*}
-H(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)) &= \sum_{t \in V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}P_{V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}(t) \log_2 P_{V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}(t)\\
&= \sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}\frac{q * P_{T_1}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))} \log_2 \frac{q * P_{T_1}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))} \\
&+ \sum_{t \in \mathcal{L}(T_2) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}\frac{(1-q) * P_{T_2}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))} \log_2 \frac{(1-q) * P_{T_2}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}
\end{align*}
We focus on the term 
$$\sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}\frac{q * P_{T_1}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))} \log_2 \frac{q * P_{T_1}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}$$
Observe that
\begin{align*}
&\sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}\frac{q * P_{T_1}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))} \log_2 \frac{q * P_{T_1}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\\
&= \frac{q}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}P_{T_1}(t) \log_2 q * P_{T_1}(t)\\
&- \frac{q * \log_2 P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}P_{T_1}(t)
\end{align*}
Again we focus on the term
$$\sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}P_{T_1}(t) \log_2 q * P_{T_1}(t)$$
Observe that
\begin{align*}
&\sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}P_{T_1}(t) \log_2 q * P_{T_1}(t) = \log_2 q * P_{T_1}(V_{\ell_1}(s))\\
& + P_{T_1}(V_{\ell_1}(s))\sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}\frac{P_{T_1}(t)}{P_{T_1}(V_{\ell_1}(s))} \log_2 \left( P_{T_1}(V_{\ell_1}(s)) *  \frac{P_{T_1}(t)}{P_{T_1}(V_{\ell_1}(s))} \right)\\
&= \log_2 q * P_{T_1}(V_{\ell_1}(s)) + \log_2 P_{T_1}(V_{\ell_1}(s)) * P_{T_1}(V_{\ell_1}(s)) + P_{T_1}(V_{\ell_1}(s))*H(V_{\ell_1}(s))\\
&= P_{T_1}(V_{\ell_1}(s))[\log_2 q + \log_2 P_{T_1}(V_{\ell_1}(s)) + H(V_{\ell_1}(s))]
\end{align*}
Hence
\begin{align*}
&\sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}\frac{q * P_{T_1}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))} \log_2 \frac{q * P_{T_1}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))} \\
&= \frac{q}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}P_{T_1}(t) \log_2 q * P_{T_1}(t)\\
&- \frac{q * \log_2 P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\sum_{t \in \mathcal{L}(T_1) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}P_{T_1}(t)\\
&= \frac{q * P_{T_1}(V_{\ell_1}(s))[\log_2 q + \log_2 P_{T_1}(V_{\ell_1}(s)) + H(V_{\ell_1}(s))]}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\\
&- \frac{q * \log_2 P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)) * P_{T_1}(V_{\ell_1}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\\
&= \frac{q * P_{T_1}(V_{\ell_1}(s)) \left[\log_2 q + \log_2 \left[\frac{P_{T_1}(V_{\ell_1}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\right] + H(V_{\ell_1}(s)) \right] }{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}
\end{align*}
Similarly,
\begin{align*}
&\sum_{t \in \mathcal{L}(T_2) \cap V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}\frac{(1-q) * P_{T_2}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))} \log_2 \frac{(1-q) * P_{T_2}(t)}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\\
&= \frac{(1-q) * P_{T_2}(V_{\ell_2}(s)) \left[\log_2 (1-q) + \log_2 \left[\frac{P_{T_2}(V_{\ell_2}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\right] + H(V_{\ell_2}(s)) \right] }{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}
\end{align*}
\begin{align*}
&-H(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))\\
&= \frac{q * P_{T_1}(V_{\ell_1}(s)) \left[\log_2 q + \log_2 \left[\frac{P_{T_1}(V_{\ell_1}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\right] + H(V_{\ell_1}(s)) \right] }{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\\
&+ \frac{(1-q) * P_{T_2}(V_{\ell_2}(s)) \left[\log_2 (1-q) + \log_2 \left[\frac{P_{T_2}(V_{\ell_2}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\right] + H(V_{\ell_2}(s)) \right] }{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}
\end{align*}
\end{enumerate}
